Plot local false sign rate results

### 2017-01-03 analysis/plot_cdf_eg.Rmd
Now generate both PDFs and PNGs in plot_lfsr.Rmd; this keeps HTML file small while also creating PDFs. Thanks to JB for suggestion.

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

*Explain here what this chunk does.*

@@

#df is a list with components method,seed, scenario
#cdf is evaluated at x
#returns list of x,y,pi0, where cdf values are in y
get_cdf = function(df,dsc=dsc_shrink,x=seq(-6,6,length=100),homedir="../code/dsc-shrink"){
  m=df$method
  if(m=="truth"){m="ash.n"}
  temp=load_example(dsc,df$seed,df$scenario,m,homedir)
  pi0=temp$meta$pi0

  if(df$method=="truth"){
    s=dsc$scenarios[[df$scenario]]
    galt=s$args$g
    g=normalmix(c(pi0,(1-pi0)*mixprop(galt)),
                c(0,comp_mean(galt)),
                c(0,comp_sd(galt)))
  } else {
    if(grepl("mixfdr",df$method)){
      temp$output= mixfdr2fitted.g(temp$output)
    }
    g=temp$output$fitted.g
  }
  data.frame(x=x,y=as.numeric(mixcdf(g,x)),pi0=pi0)
}

plot_mean_cdf = function(SEEDS,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
      PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","bimodal"),pi0filter=FALSE,...){
  PLOTNAMES = PLOTSCENARIOS
  #set up dataframe with cdf for all methods and all datasets
  df= expand.grid(seed=SEEDS,scenario=PLOTSCENARIOS, method=PLOTMETHODS,stringsAsFactors = FALSE)
  df.cdf=ddply(df,.(seed,scenario,method), get_cdf)

  if(pi0filter==TRUE){
    df.cdf %<>% filter(pi0<0.55 & pi0>0.45)
  }
  if(length(SEEDS)>1){
    df.cdf %<>% group_by(x,method,scenario) %>% dplyr::summarise(y=mean(y))
  }

  ggplot(df.cdf,aes(x=x,y=y,color=method),...) + colScale + geom_line(lwd=1.5,alpha=0.7) + facet_grid(.~scenario) + theme(legend.position = "bottom")

}
```

@@

@@

```{r mean_cdf_nopen, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr","mixfdr.tnull")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n.s","ash.u.s","ash.hu.s","truth"),pi0filter=TRUE)
source("../R/set_plot_colors.R") #reset color scale for other plots
```

@@

```{r egcdf-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
plot_mean_cdf(1,PLOTMETHODS=c("ash.n","truth"),PLOTSCENARIOS = c("spiky","near-normal","bimodal"))
```

```{r mean_cdf-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n","truth"),PLOTSCENARIOS = c("spiky","near-normal","bimodal"),pi0filter=TRUE)
```

```{r mean_cdf_nopen-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr","mixfdr.tnull")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n.s","truth"),PLOTSCENARIOS = c("spiky","near-normal","bimodal"), pi0filter=TRUE)
source("../R/set_plot_colors.R")
```

@@

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme=function(SEED=1,PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","big-normal","bimodal")){
  df=data.frame(seed=NULL,scenario=NULL,method=NULL,x=NULL,y=NULL,pi0=NULL)
  for(SCENARIO in PLOTSCENARIOS){
    temp=dscr::load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z <- REBayes::GLmix(temp$input$betahat)
    df = rbind(df,data.frame(seed=SEED,scenario=SCENARIO,method="NPMLE",x=z$x,y=cumsum(z$y)/sum(z$y),pi0=NA))
  }
  return(df)
}

>>>>

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
library(REBayes)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

TO DO: Explain here what this chunk does.

@@

# df is a list with components method,seed, scenario
# cdf is evaluated at x
# returns list of x,y,pi0, where cdf values are in y
get_cdf = function (df,dsc = dsc_shrink,x = seq(-6,6,length = 100),
                    homedir = "../code/dsc-shrink") {
  m = df$method
  if (m == "truth")
    m = "ash.n"
  temp = load_example(dsc,df$seed,df$scenario,m,homedir)
  pi0  = temp$meta$pi0

  if (df$method == "truth"){
    s    = dsc$scenarios[[df$scenario]]
    galt = s$args$g
    g    = normalmix(c(pi0,(1 - pi0) * mixprop(galt)),
                     c(0,comp_mean(galt)),
                     c(0,comp_sd(galt)))
  } else {
    if (grepl("mixfdr",df$method))
      temp$output = mixfdr2fitted.g(temp$output)
    g = temp$output$fitted.g
  }
  return(data.frame(x = x,y = as.numeric(mixcdf(g,x)),pi0 = pi0))
}

plot_mean_cdf = 
  function(SEEDS,
           PLOTMETHODS   = c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
           PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","bimodal"),
           pi0filter     = FALSE,...) {
  PLOTNAMES = PLOTSCENARIOS

  #set up dataframe with cdf for all methods and all datasets
  df     = expand.grid(seed = SEEDS,scenario = PLOTSCENARIOS,
                       method = PLOTMETHODS,stringsAsFactors = FALSE)
  df.cdf = ddply(df,.(seed,scenario,method),get_cdf)

  if (pi0filter)
    df.cdf %<>% filter(pi0 < 0.55 & pi0 > 0.45)
  if (length(SEEDS) > 1)
    df.cdf %<>% group_by(x,method,scenario) %>% summarise(y = mean(y))

  df.cdf$scenario         = factor(df.cdf$scenario,levels = PLOTSCENARIOS)
  levels(df.cdf$scenario) = PLOTNAMES

  return(ggplot(df.cdf,aes(x = x,y = y,color = method),...) + colScale + 
    geom_line(lwd = 1.5,alpha = 0.7) + facet_grid(.~scenario) + 
      theme(legend.position = "bottom"))
}
```

TO DO: Explain here what this chunk does.

@@

TO DO: Explain here what this chunk does.

@@

TO DO: Explain here what this chunk does.

```{r mean_cdf_nopen, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue",
                     "locfdr","mixfdr.tnull")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","ash.u.s","ash.hu.s","truth"),
              pi0filter = TRUE)

# Reset color scale for other plots.
source("../R/set_plot_colors.R") 
```

@@

```{r egcdf-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
plot_mean_cdf(1,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"))
```

TO DO: Explain here what this chunk does.

```{r mean_cdf-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
```

TO DO: Explain here what this chunk does.

```{r mean_cdf_nopen-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr",
                     "mixfdr.tnull")
colScale        <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
source("../R/set_plot_colors.R")
```

@@

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme = function(SEED = 1,
                     PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                                       "big-normal","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for(SCENARIO in PLOTSCENARIOS) {
    temp = dscr::load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = REBayes::GLmix(temp$input$betahat)
    df = rbind(df,data.frame(seed=SEED,scenario=SCENARIO,method="NPMLE",x=z$x,y=cumsum(z$y)/sum(z$y),pi0=NA))
  }
  return(df)
}

### 2017-01-03 analysis/plot_lfsr.Rmd
Now generate both PDFs and PNGs in plot_lfsr.Rmd; this keeps HTML file small while also creating PDFs. Thanks to JB for suggestion.

```{r plot_lfsr, dev='png', fig.width=9, fig.height=3, crop=TRUE}
print(p1 + theme(legend.position = "none",
                 axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5) + colScale)
```

@@

```{r plot_lfdr, dev='png', fig.width=9, fig.height=3, crop=TRUE}
print(p2 + theme(legend.position = "none",
                 axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5) + colScale)
```

@@

```{r plot_lfsr_s, dev='png', fig.width=9, fig.height=3, crop=TRUE}
lfsr.s = process_score_for_plotting_against_gold(res$lfsr,PLOTSEEDS = 1:100,
                                                 PLOTMETHODS = "ash.n.s")
p1.s   = plot_lfsr(lfsr.s,ylim = c(0,1),xlim = c(0,0.2))
print(p1.s + theme(legend.position = "none",
                   axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5))
```

@@

```{r plot_lfsr_s_nn, dev='png', fig.width=9, fig.height=3, crop=TRUE}
lfsr.s.nn = 
  process_score_for_plotting_against_gold(res$lfsr,PLOTSEEDS = 1:100,
    PLOTMETHODS = "ash.n.s",
    PLOTSCENARIOS = paste0(c("spiky","near-normal","flat-top","skew",
                             "big-normal","bimodal"),"-nn"))
p1.s.nn = plot_lfsr(lfsr.s.nn,ylim = c(0,1),xlim = c(0,0.2))
print(p1.s.nn + theme(legend.position = "none",
                      axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5))
```

>>>>

```{r plot_lfsr, dev=c('png','pdf'), fig.width=9, fig.height=3, crop=TRUE}
print(p1 + theme(legend.position = "none",
                 axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5) + colScale)
```

@@

```{r plot_lfdr, dev=c('png','pdf'), fig.width=9, fig.height=3, crop=TRUE}
print(p2 + theme(legend.position = "none",
                 axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5) + colScale)
```

@@

```{r plot_lfsr_s, dev=c('png','pdf'), fig.width=9, fig.height=3, crop=TRUE}
lfsr.s = process_score_for_plotting_against_gold(res$lfsr,PLOTSEEDS = 1:100,
                                                 PLOTMETHODS = "ash.n.s")
p1.s   = plot_lfsr(lfsr.s,ylim = c(0,1),xlim = c(0,0.2))
print(p1.s + theme(legend.position = "none",
                   axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5))
```

@@

```{r plot_lfsr_s_nn, dev=c('png','pdf'), fig.width=9, fig.height=3, crop=TRUE}
lfsr.s.nn = 
  process_score_for_plotting_against_gold(res$lfsr,PLOTSEEDS = 1:100,
    PLOTMETHODS = "ash.n.s",
    PLOTSCENARIOS = paste0(c("spiky","near-normal","flat-top","skew",
                             "big-normal","bimodal"),"-nn"))
p1.s.nn = plot_lfsr(lfsr.s.nn,ylim = c(0,1),xlim = c(0,0.2))
print(p1.s.nn + theme(legend.position = "none",
                      axis.text.x = element_text(size = 8,angle = 45)) +
      coord_equal(ratio = 1/5))
```
